---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Chilean ling assessment example

March 2023 external review, Valparaiso, Chile

## Analytic Approach

See @sec-model for example details describing the model and fitting approach.

### Model Selection and Evaluation

#### Example model alternatives

The @tbl-ling_mods shows some alternative model specifications and
naming convention.

| Model | Description                                                                                                                 |
|-----------------|-------------------------------------------------------|
| 1.00     | 	Patterned off of the "newer" model option presented at the review (palangre CPUE index standardized w/ PC )
| 1.01     | 	As 0.00 but with different CPUE series (as used in "base" model)

: Some model configurations described for Chilean ling (N) stock based on
data from the modified ling model in 2022. {#tbl-ling_mods}

## Results

### Fits to indices

The model fits to the index data can be seen in @fig-index_fits

```{r,eval=T}
#| label: fig-index_fits
#| warning: false
#| echo: false
#| fig-cap: "Fit to the index data"
#| fig-alt: "A line plot on a polar axis"
library(jjmR)
library(ggplot2)
library(tidyverse)
library(kableExtra)
setwd("../ling")
getwd()
theme_set(theme_jjm(base_size = 15))

m0 <- readJJM("lingN_1.00", path = "config", input = "input")
m1 <- readJJM("lingN_1.01", path = "config", input = "input")
#m1 <- readJJM("1_1.01", path = "config", input = "input")
#m2 <- readJJM("1_1.02", path = "config", input = "input")
#m3 <- readJJM("1_1.03", path = "config", input = "input")
#m4 <- readJJM("1_1.04", path = "config", input = "input")
#m5 <- readJJM("1_1.05", path = "config", input = "input")
mods <- combineModels(m0,m1)
tidy_mods <- tidy_JJM(mods)

index_fits <- tidy_mods$index_fits

index_fits %>% 
  ggplot() + 
  geom_pointrange(aes(year, observed_ind, ymin = observed_ind - 1.96 * observed_se, ymax =  observed_ind + 1.96 * observed_se), alpha = 0.5) +
  geom_path(aes(year, pred_ind, color = model)) + 
  facet_grid(model~fleet_name, scales = "free_y") + 
  scale_x_continuous(name = "Year", guide = guide_axis(n.dodge = 2)) + 
  scale_y_continuous(name = "Index Values")
```

### Fit to age composition data

The model fits to age composition data can be seen in @fig-age_comps

```{r}
#| label: fig-age_comps
#| warning: false
#| echo: false
#| fig-cap: "Observed and predicted proportions-at-age for model 4, Chilean ling (N)."
#| fig-height: 10
#| fig-width: 6
age_fits <- get_age_fits(c(m0))
age_fits %>% mutate(age=ifelse(age>9,10,age)) |> 
  filter(stock == "Stock_1", year>2010) %>% 
  pivot_longer(predicted:observed) %>% 
  ggplot() + scale_y_continuous(breaks = c(.3,.60)) +
  scale_x_continuous(breaks = 1:10) +
  geom_density(aes(age, value, linetype=name,fill = name),stat = "identity", alpha = 0.3) + 
  facet_grid(year~fleet_name)
```

### Likelihood Table

Table of likelihood values for different Chilean ling (N) model
configurations are shown in @tbl-like.

```{r }
#| label: tbl-like
#| tbl-cap: Table of likelihood values for different Chilean ling (N) model configurations. See @tbl-ling_mods for details.
LL <- cbind(summary(m0)$like,summary(m1)$like)
knitr::kable(LL) %>% kableExtra::kable_styling()
```

### Gear selectivity

Patterns in gear selectivity can be seen in @fig-selectivity

```{r}
#| label: fig-selectivity
#| fig-cap: "Fishery selectivity estimates for Chilean ling (N) model 1 and 2."
selectivities <- get_selectivities(mods[1:2])
plot_selectivities(selectivities)+ylab("Years")

```

### Trend information

The trend information can be seen at @fig-trend

```{r}
#| label: fig-trend
#| warning: false
#| echo: false
#| fig-cap: "Plots of recruitment (top) spawning biomass (middle) and totl biomass for the different Chilean ling ()N model configurations"
#| fig-height: 10
totals <- get_totals(mods) 
totals |>  
ggplot(aes(year, value, ymin=lowerbound, ymax=upperbound,fill = model, linetype = model)) +
geom_ribbon(alpha=.3) + expand_limits(y = 0) +
facet_grid(metric ~., scales = "free_y")
```

The fishing mortality rates from Model 1.04 can be seen at @fig-fs.

```{r}
#| label: fig-fs
#| warning: false
#| echo: false
#| fig-cap: "Estimates of fishing mortality for Model 1.04 of Chilean ling (N). "
#| fig-height: 7
#| fig-width: 7

fishing_mortality <- get_fishing_mortality(c(m0))
fishing_mortality %>% 
  ggplot(aes(year, mortality, color = age, group = age)) + 
  geom_line() + 
  scale_color_viridis_c() +
  facet_grid(model~. ) 
```


  
### Risk Table

The near and medium term patterns for model 1.04 are shown as an example
in @tbl-risk.

```{r results='asis'}

# From jjmR::report()
table   = summary(m0, Projections = TRUE, Fmult=c(0, "FMSY", .75, 1, 1.25))$proj[[1]]

#Nombre de la tabla: solo numeros
namesCol = colnames(table[[1]])

#Nombre de la col F. Siempre existe.
NameFs = paste0('Multiplier of \n', '$F_{', namesCol[1], '}$')

#Nombre de las col B. Depende de la longitud de BiomProj
nBiom = 3
NameBs = NULL
for(i in 1:nBiom){
  NameBs1 = c(paste0("$B_{", namesCol[i*2], "}$"), paste0("$P(B_{", namesCol[i*2+1], "}$", " > ", "$B_{MSY})$ %"))
  NameBs = c(NameBs, NameBs1)
}

#Nombre de las col C. Depende de la longitud de CapProj
nCap = 2
indName = 1 + nBiom * 2
NameCt = NULL
for(i in 1:nCap){
  NameCt1 = paste0("Catch \n", namesCol[indName + i], " (kt)")
  NameCt = c(NameCt, NameCt1)
}

###
NamesCol = c(NameFs, NameBs, NameCt)
for(i in seq_along(table)){
  colnames(table[[i]]) = NamesCol  
}
```

```{r}
#| label: tbl-risk
#| warning: true
#| echo: false
#| tbl-cap: "Table of estimated stock risks for spawning biomass and catch for Model 1.04 of Chilean ling (N). "
knitr::kable(table[[1]], format='html',
             align="c",escape=FALSE) %>% kableExtra::kable_styling(
  latex_options = c("HOLD_position", "scale_down")) #%>% 
 #col.names = c("Grouping", "$M$", "$SD$", "N", "$\\eta$"), escape = FALSE) %>%

```

### Retrospective plots

```{r}
#plot(mods[2:3], var="SSB") # only SSB

```

### Kobe plots

```{r}
#| label: fig-kobe
#| fig-cap: "KOBE plots for different stock-recruitment relationships (models 1.03 and model 1.04) for Chilean ling (N). See @tbl-ling_mods for model descriptions."
msy_my_results = get_msy_mt(mods)
kobe(mods[1:2], engine = "ggplot",overlay=TRUE)
```


### Stock projections

The @fig-proj shows
The @fig-proj2 shows

```{r}
#| label: fig-proj 
#| echo: false
#| fig-cap: "Stock projections for different assumed future fishing mortality rates for Chilean ling (N), model 1.04)."
m0_diag <- diagnostics(m0)
plot(m0_diag, var = "ssbPrediction")
```

```{r}
#| label: fig-proj2
#| echo: false
#| fig-cap: "Stock projections for different assumed future fishing mortality rates for Chilean ling (N), model 1.04)."
plot(m0_diag, var = "catchPrediction")
```


## Literature Cited

Include citations that are relevant to understanding the stock and its
status, but are not cited in the report in a special "extra references"
section.  